Diagnosing Child Poverty Reduction Interventions

### 2024-09-05 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Added plots for mean and median hh_income by quintile - 2 different quintile calculations

library(tidyverse)
library(ggplot2)
library(ggridges) # for densities over time plots. 
library(knitr)
library(here)
library(gghighlight)

@@

@@

>>>>

library(tidyverse)
library(ggplot2)
library(ggridges) # for densities over time plots. 
library(knitr)
library(here)
library(gghighlight)
library(spatstat)

@@

## Density Ridges

@@

## Mean Income

```{r}
mean_income_quintile <- function(base, int) {
  base <- base %>%
    select(pidp, time, hh_income, income_quint, weight) %>%
    mutate(source = 'Baseline')
  int <- int %>%
    select(pidp, time, hh_income, income_quint, weight) %>%
    mutate(source = 'Intervention')

  combined <- rbind(base, int)

  combined <- combined %>%
    group_by(time, income_quint, source) %>%
    summarise(mean = weighted.mean(hh_income, weight),
              median = weighted.median(hh_income, weight))

  combined$income_quint <- factor(combined$income_quint)
  combined$source <- factor(combined$source)

  p1 <- ggplot(combined, aes(x = time, y = mean, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
    geom_line() +
    labs(title = 'Mean hh_income by quintile',
         subtitle = 'Baseline vs Intervention')

  p2 <- ggplot(combined, aes(x = time, y = median, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
    geom_line() +
    labs(title = 'Median hh_income by quintile',
         subtitle = 'Baseline vs Intervention')

  print(p1)
  print(p2)
  #return(p)
}

mean_income_quintile(base.dat, int.dat)
```

```{r}
mean_income_quintile_2 <- function(base, int) {

  base <- base.dat %>%
    select(pidp, time, hh_income, income_quint, weight) %>%
    mutate(source = 'Baseline')

  # start processing to use baseline income_quint var on intervention
  base.tmp <- base %>% 
    select(-weight, -hh_income, -source)

  int <- int.dat %>%
    select(pidp, time, hh_income, weight)

  merged.int <- merge(int, base.tmp, by = c('pidp', 'time'))

  int <- merged.int %>%
    mutate(source = 'Intervention')

  combined <- rbind(base, int)

  combined <- combined %>%
    group_by(time, income_quint, source) %>%
    summarise(mean = weighted.mean(hh_income, weight),
              median = weighted.median(hh_income, weight))

  combined$income_quint <- factor(combined$income_quint)
  combined$source <- factor(combined$source)

  p1 <- ggplot(combined, aes(x = time, y = mean, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
    geom_line() +
    labs(title = 'Mean hh_income by quintile',
         subtitle = 'Baseline vs Intervention')

  p2 <- ggplot(combined, aes(x = time, y = median, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
    geom_line() +
    labs(title = 'Median hh_income by quintile',
         subtitle = 'Baseline vs Intervention')

  print(p1)
  print(p2)
  #return(p)
}

mean_income_quintile_2(base.dat, int.dat)
```
